%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Document Class
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass{notes}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Packages
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{cpp}
\usepackage{verbatim}
\usepackage{lastpage}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% New Commands
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Macros
\newcommand{\github}{\link{http://www.github.com/mwhittaker/beejsockets}{beejsockets github}}
\newcommand{\listing}[1]{../listings/#1}
\newcommand{\src}[1]{../src/#1}
\newcommand{\imgpath}[1]{../res/img/#1}

%% Listing reference
% Reference listings.
\newcommand{\listref}[1]{Listing~\ref{list:#1}}

%% Figure reference
% Reference figures
\newcommand{\figref}[1]{Figure~\ref{fig:#1}}

%% Title page
\renewcommand*{\titlepage}{\begingroup
\raggedleft
\vspace*{\baselineskip}
{\Large Michael Whittaker}\\[0.167\textheight]
{\textcolor{blue}{\Huge Beej's Guide to Network Programming}}\\[\baselineskip] 
{\Large \textit{Thoughts and Notes}}\par
\vfill
{\large \github{}}\par
\vspace*{3\baselineskip}
\endgroup}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Document
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%% Title Page
\thispagestyle{empty}
\titlepage
\newpage

%% Table of Contents
\tableofcontents
\newpage

%% List of listings
\lstlistoflistings
\newpage

%% Preface
\subsection*{Preface}
This document contains the notes, musings, and thoughts generated during my reading of ``Beej's Guide to Network Programming'' by Brian Hall. The notes were taken primarily to encourage a thorough reading of the book and to help me recall the most important tidbits from the book upon a rereading of my notes. I can imagine the notes may be helpful to more than just me, so I am making them publicly available. A network programming novice, I cannot guarantee my notes are entirely correct, or even sensical at times. If you ever encounter a mistake, please contact me at mjw297@cornell.edu.

Along with the notes, I've thrown together some source code and other resources. Some of the code is taken directly from the text while some is original. All notes, code, and resources can be found at the \github{}.

Enjoy!
\newpage  

%% Chapters
\input{chapter1.tex}
\newpage

\input{chapter2.tex}
\newpage

\input{chapter3.tex}
\newpage

\input{chapter4.tex}
\newpage

\input{chapter5.tex}
\newpage

\input{chapter6.tex}
\newpage

\input{chapter7.tex}


\end{document}
